---
title: "plot Jump-seq reads distribution of spike-in"
output: html_document
Author: Yuwen Liu
---

Reads distribution on spike-in sequences, Deduplicate reads based on UMI info. 
analyze with 160811 data. 
compare distribution with default mapping or mapping allowing mismatch on the 1st base of each read


```{r,echo=FALSE}
setwd("/media/yuwen/Elements/Tiao_Seq/analysis")
source("../lib/draw_reads_distribution.R")
knitr::opts_chunk$set(fig.width = 10,fig.height = 5)
options(warn=-1)
```

\newpage


```{r,echo=FALSE,fig.width=5,fig.height=5}
#plus reads and minus sites

a = read.delim("../data/Data/160811/20160811_5hmC_Jump_Seq_1.2ng.5hmc_spike_in.umi_encoded_adaptor_removed.sorted.dedup.bam.minus.sorted.5prime.bed.coverage.ave.perbase", header = FALSE, sep = "\t", stringsAsFactors = FALSE)

b = read.delim("../data/Data/160811/20160811_5hmC_Jump_Seq_0.6ng.5hmc_spike_in.umi_encoded_adaptor_removed.sorted.dedup.bam.minus.sorted.5prime.bed.coverage.ave.perbase", header = FALSE, sep = "\t", stringsAsFactors = FALSE)


c = read.delim("../data/Data/160811/20160811_5mC_Jump_Seq_48ng.5mc_spike_in.umi_encoded_adaptor_removed.sorted.dedup.bam.minus.sorted.5prime.bed.coverage.ave.perbase", header = FALSE, sep = "\t", stringsAsFactors = FALSE)


d = read.delim("../data/Data/160811/20160811_5mC_Jump_Seq_24ng.5mc_spike_in.umi_encoded_adaptor_removed.sorted.dedup.bam.minus.sorted.5prime.bed.coverage.ave.perbase", header = FALSE, sep = "\t", stringsAsFactors = FALSE)

e = read.delim("../data/Data/160811/20160811_5mC_Jump_Seq_12ng.5mc_spike_in.umi_encoded_adaptor_removed.sorted.dedup.bam.minus.sorted.5prime.bed.coverage.ave.perbase", header = FALSE, sep = "\t", stringsAsFactors = FALSE)

f = read.delim("../data/Data/160811/20160811_5mC_Jump_Seq_6ng.5mc_spike_in.umi_encoded_adaptor_removed.sorted.dedup.bam.minus.sorted.5prime.bed.coverage.ave.perbase", header = FALSE, sep = "\t", stringsAsFactors = FALSE)

g = read.delim("../data/Data/160811/20160811_5mC_Jump_Seq_2.4ng.5mc_spike_in.umi_encoded_adaptor_removed.sorted.dedup.bam.minus.sorted.5prime.bed.coverage.ave.perbase", header = FALSE, sep = "\t", stringsAsFactors = FALSE)



data = cbind(a,b,c,d,e,f,g)

test = orgnize_table(data,7,c("5hmc-1.2ng","5hmc-0.6ng","5mc-48ng","5mc-24ng","5mc-12ng","5mc-6ng","5mc-2.4ng"),seq(-98,101,1),c(1,200))

```

* plus sites and minus reads, raw reads distribution

```{r,echo=FALSE,fig.width=10,fig.height=5}
draw_plot_together(test,mode = "original",-100, 101)
```

```{r,echo=FALSE,fig.width=10,fig.height=6}
draw_plot_separate(test,mode = "original",-100, 101)
```

\newpage

* plus sites and minus reads, normalized reads distribution

```{r,echo=FALSE,fig.width=10,fig.height=5}
draw_plot_together(test,mode = "normalized",-100, 101)
```

```{r,echo=FALSE,fig.width=10,fig.height=6}
draw_plot_separate(test,mode = "normalized",-100, 101)
```

\newpage

```{r,echo=FALSE}
test = orgnize_table(data,7,c("5hmc-1.2ng","5hmc-0.6ng","5mc-48ng","5mc-24ng","5mc-12ng","5mc-6ng","5mc-2.4ng"),seq(-98,101,1),c(50,150))

```

* plus sites and minus reads, raw reads distribution

```{r,echo=FALSE,fig.width=10,fig.height=5}
draw_plot_together(test,mode = "original",-50, 50)
```



```{r,echo=FALSE,fig.width=10,fig.height=6}
draw_plot_separate(test,mode = "original",-50, 50)
```

\newpage
* plus sites and minus reads, normalized reads distribution, removing reads at two ends before normalization

```{r,echo=FALSE,fig.width=10,fig.height=5}
draw_plot_together(test,mode = "normalized",-50, 50)
```

```{r,echo=FALSE,fig.width=10,fig.height=6}
draw_plot_separate(test,mode = "normalized",-50, 50)
```
