---
title: "Distinct reads saturation analysis of previous 5hmc data. "
output: html_document
---

***

##### The first 5 plots are 48ng samples, the last plot is 2.4ng sample

```{r,echo=FALSE}
source("../lib/distinct_reads_saturation_analysis.R")
```


> <span style="color:red; font-family:arial; font-size:1em;">He-lu-6_S6_L006_R1_001.umi_encoded_adaptor_removed_no_mismatch</span>


```{r,echo=FALSE,cache=TRUE}
temp = draw_mapped_dedup_reads_single_cell("He-lu-6_S6_L006_R1_001.umi_encoded_adaptor_removed_no_mismatch","../processed_files/160402/")
p = ggplot(temp)+geom_line(aes(x=sub_sample, y = distinct_reads))+theme(axis.text.x = element_text(size =10, color = "black",hjust = 1, vjust = 1), axis.text.y = element_text(size =10, color = "black"))
p
```

> <span style="color:red; font-family:arial; font-size:1em;">CHe-Lu-1_S12_L005_R1_001.umi_encoded_adaptor_removed_no_mismatch</span>


```{r,echo=FALSE,cache=TRUE}
temp = draw_mapped_dedup_reads_single_cell("CHe-Lu-1_S12_L005_R1_001.umi_encoded_adaptor_removed_no_mismatch","../processed_files/160511/")
p = ggplot(temp)+geom_line(aes(x=sub_sample, y = distinct_reads))+theme(axis.text.x = element_text(size =10, color = "black",hjust = 1, vjust = 1), axis.text.y = element_text(size =10, color = "black"))
p
```

> <span style="color:red; font-family:arial; font-size:1em;">He-Lu-lu-1-48ng_S1_L006_R1_001.umi_encoded_adaptor_removed_no_mismatch</span>


```{r,echo=FALSE,cache=TRUE}
temp = draw_mapped_dedup_reads_single_cell("He-Lu-lu-1-48ng_S1_L006_R1_001.umi_encoded_adaptor_removed_no_mismatch","../processed_files/160521/")
p = ggplot(temp)+geom_line(aes(x=sub_sample, y = distinct_reads))+theme(axis.text.x = element_text(size =10, color = "black",hjust = 1, vjust = 1), axis.text.y = element_text(size =10, color = "black"))
p
```

> <span style="color:red; font-family:arial; font-size:1em;">20160601_5hmC_Jump_Seq_48ng.umi_encoded_adaptor_removed_no_mismatch.bam</span>


```{r,echo=FALSE,cache=TRUE}
temp = draw_mapped_dedup_reads_single_cell("20160601_5hmC_Jump_Seq_48ng.umi_encoded_adaptor_removed_no_mismatch","../processed_files/160604/")
p = ggplot(temp)+geom_line(aes(x=sub_sample, y = distinct_reads))+theme(axis.text.x = element_text(size =10, color = "black",hjust = 1, vjust = 1), axis.text.y = element_text(size =10, color = "black"))
p
```

> <span style="color:red; font-family:arial; font-size:1em;">He-Lu-6_48ng-S3_L001_R1_001.umi_encoded_adaptor_removed_no_mismatch</span>


```{r,echo=FALSE,cache=TRUE}
temp = draw_mapped_dedup_reads_single_cell("He-Lu-6_48ng-S3_L001_R1_001.umi_encoded_adaptor_removed_no_mismatch","../processed_files/160620/")
p = ggplot(temp)+geom_line(aes(x=sub_sample, y = distinct_reads))+theme(axis.text.x = element_text(size =10, color = "black",hjust = 1, vjust = 1), axis.text.y = element_text(size =10, color = "black"))
p
```

> <span style="color:red; font-family:arial; font-size:1em;">CHe-Lu-5_S20_L005_R1_001.umi_encoded_adaptor_removed.sorted</span>


```{r,echo=FALSE,cache=TRUE}
temp = draw_mapped_dedup_reads_single_cell("CHe-Lu-5_S20_L005_R1_001.umi_encoded_adaptor_removed.sorted","../processed_files/160511/")
p = ggplot(temp)+geom_line(aes(x=sub_sample, y = distinct_reads))+theme(axis.text.x = element_text(size =10, color = "black",hjust = 1, vjust = 1), axis.text.y = element_text(size =10, color = "black"))
p
```