---
title: "Overlap of 0.6ng 6hmc reads with 48ng hmc peaks"
output: html_document
---

***
* Identify 1kb regions enriched for Jump-Seq reads by using pooled reads from all 11 48ng biological replicates (FDR < 0.05). These windows could serve as gold standard/true positive. 
* Count the reads coverage in these 1kb windows using rep1 and rep2, respectively.
* Plot the coverage across rep1 and rep2 and calculate the correlation coefficient between rep1 and rep2. 

***


## plus reads 

```{r,cache=TRUE, echo=FALSE}
a <- read.delim("../unified_data_repo/reps_combine_5hmc/combine11rep.plus.1001.bp.FDR0.05.rep1.coverage", header = FALSE, sep = "\t", stringsAsFactors = FALSE)
a <- a[,4]
b <- read.delim("../unified_data_repo/reps_combine_5hmc/combine11rep.plus.1001.bp.FDR0.05.rep2.coverage", header = FALSE, sep = "\t", stringsAsFactors = FALSE)
b <- b[,4]

```

```{r, fig.width=5, fig.height=5}
# correlation coefficient
cor(a,b)
# correlation coefficient, log2 transformed
cor(log(a+1,2),log(b+1,2))
# plot
plot(log(a,2),log(b,2), xlab = "rep1", ylab = "rep2")
```

## minus reads

```{r,cache=TRUE, echo=FALSE}
c <- read.delim("../unified_data_repo/reps_combine_5hmc/combine11rep.minus.1001.bp.FDR0.05.rep1.coverage", header = FALSE, sep = "\t", stringsAsFactors = FALSE)
c <- c[,4]

d <- read.delim("../unified_data_repo/reps_combine_5hmc/combine11rep.minus.1001.bp.FDR0.05.rep2.coverage", header = FALSE, sep = "\t", stringsAsFactors = FALSE)
d <- d[,4]
```

```{r,fig.width=5, fig.height=5}
# correlation coefficient
cor(c,d)
# correlation coefficient, log2 transformed
cor(log(c+1,2),log(d+1,2))
# plot
plot(log(c,2),log(d,2), xlab = "rep1", ylab = "rep2")
```
